FraCaS: Temporal Analysis

### 2020-06-04 paper2020/paper.tex
salvage previous commit

\section{Conclusions and Future Work}
We have presented a first attempt for a computational approach dealing with the temporal section of the FraCaS test suite. This is the first time a system is ran against this section, at the same time, this concludes our work in handling the whole of the FraCaS test suite using a combination of a number of well-studied tools: type theory, Grammatical Framework, Monadic Dynamic Semantics and proof assistant technology (Coq). 
\section*{Acknowledgements}

>>>>

\section{Conclusions and Future Work}
We have presented a first attempt for a computational approach dealing with the temporal section of the FraCaS test suite. This is the first time a system is ran against this section, at the same time, this concludes our work in handling the whole of the FraCaS test suite using a combination of a number of well-studied tools: type theory, parsing using the Grammatical Framework (GF), Monadic Dynamic Semantics and proof assistant technology (Coq). It achieves an accuracy of 0.71 on the Temporal Section and 0.78 overall. One of the things to be looked at is fixing the issues associated with parts of the test suite that ``broke'' so to say when the temporal analysis was introduced. Some of these have been already mentioned: interaction of the temporal variables with group readings and negation.

Another issue to be looking at is the codification of lexical aspect. In what we have been doing so far, we did not distinguish between the present continuous and the present or the simple past and the past continuous and their interaction with non-lexical aspect.  The main reason for this  is that in the test suite, even though there are examples of inferences based on the either lexical or non-lexical aspect, no example where an interaction between the two exists. For example, one such case is the one shown below and exemplifies the difference between activities and accomplishments with respect to the different inferences they give when used  in the past continuous:

\fracasex{extra1}{
	\item	John was writing a book. 
	\hyp 	John wrote a book (UNK).
}

\fracasex{extra2}{
	\item	John was running. 
	\hyp 	John ran (YES).
}

\fracasex{extra1}{
	\item	John wrote a book. 
	\hyp 	John was writing a book (YES).
}

\fracasex{extra2}{
	\item	John ran. 
	\hyp 	John was running (YES?).
}

\section*{Acknowledgements}
